Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-03-30 paper/paper-nature_format.tex
updated zenodo link

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro and micro-level text analysis because it has only been
available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures all
proceedings of the Australian parliamentary debates from 1998 to the
present using Hansard. The database is publicly available and can be
linked to other datasets such as election results. The creation and
accessibility of this database enables the exploration of questions that
have not been possible to explore, serving as a valuable resource for
both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

Our database contains 1517 CSV files, covering all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022. All
data records are available on the general-purpose repository Zenodo, at
https://doi.org/10.5281/zenodo.7336076 (Katz and Alexander 2022). For
each CSV file, each row contains an individual statement, with details
on the individual speaking. Of course, for general statements
transcribed as made by ``Honourable members'' for example, these
variables cannot be specified. Table~\ref{tbl-vars} provides an overview
of each variable found in the database.

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2022}{}}%
Katz, Lindsay, and Rohan Alexander. 2022. {``{A new, comprehensive
database of all proceedings of the Australian Parliamentary Debates}.''}
Zenodo. \url{https://doi.org/10.5281/zenodo.7336076}.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro and micro-level text analysis because it has only been
available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures all
proceedings of the Australian parliamentary debates from 1998 to the
present using Hansard. The database is publicly available and can be
linked to other datasets such as election results. The creation and
accessibility of this database enables the exploration of questions that
have not been possible to explore, serving as a valuable resource for
both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Our database contains 1517 CSV files, covering all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022. All
data records are available on the general-purpose repository Zenodo, at
https://doi.org/10.5281/zenodo.7785767 (Katz and Alexander 2023). For
each CSV file, each row contains an individual statement, with details
on the individual speaking. Of course, for general statements
transcribed as made by ``Honourable members'' for example, these
variables cannot be specified. Table~\ref{tbl-vars} provides an overview
of each variable found in the database.

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
database of all proceedings of the Australian Parliamentary Debates
(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7785767}.
